---
title: "OSF Preprint Assertions"
date: "2025-08-12"
date-modified: last-modified
---

# Overview

This method measures lifecycle open science on OSF by looking at preprint assertions linked to open science preprints.

## Definitions

> **OSP**Open Science Preprint (OSP): An OSF Preprint that is jointly *open*, *non-deprecated*, and *authentic*

- Openness Criteria:
    1. Public (open-1)

- Non-Deprecation Criteria:
    1. Accepted (nondeprecated-1)
    2. Published (nondeprecated-2)
    3. Not Deleted (nondeprecated-3)
    4. Not Withdrawn (nondeprecated-4)

- Authenticity Criteria:
    1. Not Spam (authentic-1)

>  **LOS-Preprint**: An OSP that represents a lifecycle open science research project.

- Lifecycle Open Criteria:

    1. **Plan**: The OSP has at least 1 linked preregistration
    2. **Output**: The OSP has at least 1 linked dataset


# Results

```{r}
# Packages
library(arrow)
library(ggplot2)
library(ggiraph)
library(glue)
library(gt)
library(dplyr)
library(lubridate)
library(plotly)
library(scales)
library(tidyr)
library(timetk)

# Modules
box::use(
  R / plot[pivoter, ppt_factorizer, ts_prep],
  R / parameters[DATES]
)



# Local functions
table_helper <- function(tbl, title  = "Lifecycle Open Science Preprints", interactive = TRUE, ...) {
    gtbl <- tbl |>
        gt() |>
        tab_header(title = title,
        subtitle = paste0("as of ", MOST_RECENT_CHR)
    ) |>
    fmt_number(columns = c(OSP:`LOS-Preprint`), decimals = 0) |>
    fmt_percent(columns = `LOS-Preprint / OSP`, decimals = 2) |>
    tab_footnote(
        footnote = md("*OSP: Open Science Preprint*"),
        locations = cells_column_labels(columns = OSP)
    ) |>
    tab_footnote(
        footnote = md("*LOS-Preprint: Lifecycle Open Science Preprint*"),
        locations = cells_column_labels(columns = `LOS-Preprint`)
    ) |>
    opt_footnote_marks("letters") |>
    opt_row_striping(row_striping = TRUE) 

    if (interactive) {
        gtbl |>
            opt_interactive(...) |>
            opt_horizontal_padding(0)
    } else {
        gtbl
    }
}


tte_table <- function(tbl, title = "Time to Lifecycle Open Status (in days)", group_label = NULL, ...) {
  # Set title
  TITLE <- "Time to Lifecycle Open Status (in days)"
  if (!is.null(group_label)) {
    TITLE <- paste0(TITLE, " by ", stringr::str_to_title(group_label))
  }

  # Subset data
  tbl <- tbl |>
    select(..., event, n, p, mean, p50, sd, min, max) |>
    filter(tolower(event) %in% c("output", "outcome", "lifecycle")) |>
    mutate(
      event = stringr::str_to_title(event),
      event = factor(event, levels = c("Output", "Outcome", "Lifecycle"))
    ) |>
    arrange(event) |>
    mutate(event = as.character(event))

  # Format table
  gtbl <- tbl |>
    gt(row_group_as_column = TRUE) |>
    tab_header(
      title = TITLE,
      subtitle = "Among all Open Science Preprints (OSP)") |>
    cols_label(
      event = "Event",
      n = "Count",
      p = "Percent",
      mean = "Mean",
      p50 = "Median",
      sd = "Std. Dev.",
      min = "Min",
      max = "Max"
    ) |>
    #Spanners
    tab_spanner(columns = c(n, p), label = "Prevalance") |>
    tab_spanner(columns = c(mean, p50, sd, min, max), label = "Distribution") |>
    # Value formatting
    fmt_number(columns = c(n, mean, p50, sd, min, max), decimals = 0) |>
    fmt_percent(columns = p, decimals = 1)
  # Return table
  gtbl
}


# Data sources
all_ts <- read_parquet(here::here("data/preprint_tsmonthly.parquet"))
provider_ts <- read_parquet(here::here("data/preprint_providers_tsmonthly.parquet"))

# Pivot for plots and assign labels
all_summary <- pivoter(all_ts) |>
    ts_prep()
provider_summary <- pivoter(provider_ts, provider) |>
    ts_prep()

# Constants
MOST_RECENT_CHR <- max(all_ts$date)
MOST_RECENT <- ymd(MOST_RECENT_CHR)
TABLE_CRITERIA <- c(
    "los_outcome", "los_plans", "los_outputs", "los_complete")
TABLE_NAMES <- c(
    "OSP", "OSP + Plan(s)", "OSP + Output(s)", "LOS-Preprint"
)
```

## Today
Here is the current state of LOS research projects on the OSF as of `r max(all_ts$date)`.  For all of the summary tables below, the following fields are included:

- `<GROUP_NAME>`: An optional grouping variable for seeing disaggregated results (e.g., by provider, institutional membership, etc.)
- `OSP`: Number of Open Science Preprints (i.e., Open + Non-deprecated + Authentic)
- `OSP + Plan`: Number of Open Science Preprints with at least one linked output resource
- `OSP + Outcome(s)`: Number of Open Science Preprints with at least one linked outcome resource
- `LOS-Preprint`: Lifecycle Open Science Preprints - number of Open Science Preprints with at least one linked outcome and at least one linked output resource
- `LOS-Preprint / OSP`: Percentage of Open Science OSF Preprints (OSP) that are Lifecycle Open Science Preprints (LOS-Preprint)


### Aggregate

```{r}
overall_tbl <- all_summary |>
    filter(criteria %in% TABLE_CRITERIA) |>
    pivot_wider(names_from = criteria, values_from = n) 
names(overall_tbl) <-c("Date", TABLE_NAMES)

overall_tbl <- overall_tbl |>
    mutate(
        `LOS-Preprint / OSP` = `LOS-Preprint` / `OSP`,
    )

today_gtbl <- overall_tbl |>
    filter(Date == MOST_RECENT) |>
    select(-Date) |>
    table_helper("Lifecycle Open Science Preprints", use_pagination = FALSE, use_sorting = FALSE)

today_gtbl
```

### By Provider

```{r}
provider_tbl <- provider_summary |>
    filter(criteria %in% TABLE_CRITERIA) |>
    pivot_wider(names_from = criteria, values_from = n) 
names(provider_tbl) <-c("Date", "Provider", TABLE_NAMES)

provider_tbl <- provider_tbl |>
    mutate(
        `LOS-Preprint / OSP` = `LOS-Preprint` / `OSP`,
    )

today_provider_tbl <- provider_tbl |>    
    filter(Date == MOST_RECENT) |>
    select(-Date) |>    
    table_helper("Lifecycle Open Science Preprints by Provider", use_pagination = FALSE)

today_provider_tbl
```


## Time to Lifecycle Open Science

PENDING
