---
title: "OSF Registration Badges"
date: "2025-09-15"
date-modified: last-modified
---

# Overview

This method measures lifecycle open science on OSF by looking at open science practices linked to open science registrations.  

## Definitions

> **Open Science Registration (OSR)**: An OSF Registration that is jointly *open*, *non-deprecated* and *authentic*

- Openness Criteria:
    1. Public (open-1)
    2. ~~Not Embargoed (open-2)~~

- Non-Deprecation Criteria:
    1. Registered (nondeprecated-1)
    2. Not Deleted (nondeprecated-2)
    3. Not Retracted (nondeprecated-3)

- Authenticity Criteria:
    1. Not Spam (authentic-1)


> **LOS-Reg**: An OSR that represents a lifecycle open science research project.

- Lifecycle Opennness Criteria:

    1. **Output** - The OSR has at least 1 linked [Open Practice Resource](https://help.osf.io/article/452-open-practice-badges) from among: "Data", "Analytic Code", "Materials" or "Supplements".  
    2. **Outcome** - The OSR has at least 1 linked "Papers" Open Practice Resource.


# Results
```{r}
# Packages
library(arrow)
library(ggplot2)
library(ggiraph)
library(glue)
library(gt)
library(dplyr)
library(lubridate)
library(plotly)
library(scales)
library(tidyr)
library(timetk)


# Modules
box::use(
  R / helpers[tidy_registry_names, tidy_template_names],
  R / plot[pivoter, factorizer, ts_prep],
  R / parameters[DATES, OUTPUTS, OUTCOMES]
)

OUTPUTS <- stringr::str_to_title(OUTPUTS)
OUTCOMES <- stringr::str_to_title(OUTCOMES)

# Local functions
table_helper <- function(tbl, title  = "Lifecycle Open Science Registrations", interactive = TRUE, ...) {
    gtbl <- tbl |>
        gt() |>
        tab_header(title = title,
        subtitle = paste0("as of ", MOST_RECENT_CHR)
    ) |>
    fmt_number(columns = c(OSR:`LOS-Reg`), decimals = 0) |>
    fmt_percent(columns = `LOS-Reg / OSR`, decimals = 2) |>
    tab_footnote(
        footnote = md("*OSR: Open Science Registration*"),
        locations = cells_column_labels(columns = OSR)
    ) |>
    tab_footnote(
        footnote = md("*LOS-Reg: Lifecycle Open Science Registration*"),
        locations = cells_column_labels(columns = `LOS-Reg`)
    ) |>
    opt_footnote_marks("letters") |>
    opt_row_striping(row_striping = TRUE) 

    if (interactive) {
        gtbl |>
            opt_interactive(...) |>
            opt_horizontal_padding(0)
    } else {
        gtbl
    }
}


tte_table <- function(tbl, title = "Time to Lifecycle Open Status (in days)", group_label = NULL, ...) {
  # Set title
  TITLE <- "Time to Lifecycle Open Status (in days)"
  if (!is.null(group_label)) {
    TITLE <- paste0(TITLE, " by ", stringr::str_to_title(group_label))
  }

  # Subset data
  tbl <- tbl |>
    select(..., event, n, p, mean, p50, sd, min, max) |>
    filter(tolower(event) %in% c("output", "outcome", "lifecycle")) |>
    mutate(
      event = stringr::str_to_title(event),
      event = factor(event, levels = c("Output", "Outcome", "Lifecycle"))
    ) |>
    arrange(event) |>
    mutate(event = as.character(event))

  # Format table
  gtbl <- tbl |>
    gt(row_group_as_column = TRUE) |>
    tab_header(
      title = TITLE,
      subtitle = "Among all Open Science Registrations (OSR)") |>
    cols_label(
      event = "Event",
      n = "Count",
      p = "Percent",
      mean = "Mean",
      p50 = "Median",
      sd = "Std. Dev.",
      min = "Min",
      max = "Max"
    ) |>
    #Spanners
    tab_spanner(columns = c(n, p), label = "Prevalance") |>
    tab_spanner(columns = c(mean, p50, sd, min, max), label = "Distribution") |>
    # Value formatting
    fmt_number(columns = c(n, mean, p50, sd, min, max), decimals = 0) |>
    fmt_percent(columns = p, decimals = 1)
  # Return table
  gtbl
}



# Data sources
all_ts <- read_parquet(here::here("data/registration_tsmonthly.parquet")) |>
    filter(date >= "2022-08-01")
registry_ts <- read_parquet(here::here("data/registration_registries_tsmonthly.parquet")) |>
    filter(date >= "2022-08-01") |>
    mutate(registry = tidy_registry_names(registry))
template_ts <- read_parquet(here::here("data/registration_templates_tsmonthly.parquet")) |>
    filter(date >= "2022-08-01") |>
    mutate(template = tidy_template_names(template)) |>
    group_by(date, template) |>
    summarise_all(sum) 

# Pivot for plots and assign labels
all_summary <- pivoter(all_ts) |>
    ts_prep()
registry_summary <- pivoter(registry_ts, registry) |>
    ts_prep()
template_summary <- pivoter(template_ts, template) |>
    ts_prep()

# Constants
MOST_RECENT_CHR <- max(all_ts$date)
MOST_RECENT <- ymd(MOST_RECENT_CHR)
TABLE_CRITERIA <- c(
    "los_plan", "los_outputs", "los_outcomes", "los_complete")
TABLE_NAMES <- c(
    "OSR", "OSR + Output(s)", "OSR + Outcome(s)","LOS-Reg"
)
```

## Today

Here is the current state of LOS research projects on the OSF as of `r max(all_ts$date)`.  For all of the summary tables below, the following fields are included:

- `<GROUP_NAME>`: An optional grouping variable for seeing disaggregated results (e.g., by registry, registration template, etc.)
- `OSR`: Number of Open Science Registrations (i.e., Open + Non-deprecated + Authentic)
- `OSR + Output(s)`: Number of Open Science Registrations with at least one linked output resource
- `OSR + Outcome(s)`: Number of Open Science Registrations with at least one linked outcome resource
- `LOS-Reg`: Lifecycle Open Science Registrations - number of Open Science Registrations with at least one linked outcome and at least one linked output resource
- `LOS-Reg / OSR`: Percentage of Open Science OSF Registrations (OSR) that are Lifecycle Open Science Registrations (LOS-Reg)


### Aggregate

```{r}
overall_tbl <- all_summary |>
    filter(criteria %in% TABLE_CRITERIA) |>
    pivot_wider(names_from = criteria, values_from = n) 
names(overall_tbl) <-c("Date", TABLE_NAMES)

overall_tbl <- overall_tbl |>
    mutate(
        `LOS-Reg / OSR` = `LOS-Reg` / `OSR`,
    )

today_gtbl <- overall_tbl |>
    filter(Date == MOST_RECENT) |>
    select(-Date) |>
    table_helper("Lifecycle Open Science Registrations", use_pagination = FALSE, use_sorting = FALSE)

today_gtbl
```

### By Registry

```{r}
registry_tbl <- registry_summary |>
    filter(criteria %in% TABLE_CRITERIA) |>
    pivot_wider(id_cols = c(date, registry), names_from = criteria, values_from = n) 
names(registry_tbl) <-c("Date", "Registry", TABLE_NAMES)

registry_tbl <- registry_tbl |>
    mutate(
        `LOS-Reg / OSR` = `LOS-Reg` / `OSR`,
    )

today_registry_gtbl <- registry_tbl |>
    ungroup() |>
    filter(Date == MOST_RECENT) |>
    arrange(desc(`LOS-Reg`)) |>
    select(-Date) |>
    table_helper("Lifecycle Open Science Registrations by Registry", use_pagination = FALSE)

today_registry_gtbl
```

### By Template

```{r}
template_tbl <- template_summary |>
    filter(criteria %in% TABLE_CRITERIA) |>
    pivot_wider(id_cols = c(date, template), names_from = criteria, values_from = n) 
names(template_tbl) <-c("Date", "Template", TABLE_NAMES)

template_tbl <- template_tbl |>
    mutate(
        `LOS-Reg / OSR` = `LOS-Reg` / `OSR`
    )

today_template_gtbl <- template_tbl |>
    ungroup() |>
    filter(Date == MOST_RECENT) |>
    arrange(desc(`LOS-Reg`)) |>
    select(-Date) |>
    table_helper("Lifecycle Open Science Registrations by Template", use_search = TRUE)

today_template_gtbl
```

## Time to Lifecycle Open Status


```{r}
# TODO: Compute date of OSR status from logged event tables, not just current status
reg_tbl <- read_parquet(here::here("data/registration_current.parquet")) |>
    filter(is_osr == 1) |>
    select(node_id, registry, registered_date) 
reg_events <- read_parquet(here::here("data/registration_badges_ttlos.parquet")) |>
    inner_join(reg_tbl, by = "node_id", relationship = "many-to-one")


#' Time to event summarizer
tte_summarizer <- function(tbl, t = time_to_event, x = event, ...) {
    # Totals
    df_n <- tbl |>
        summarize(
            .by = c(...),
            N = n_distinct(node_id)
        ) |>
        cross_join(distinct(tbl, {{ x }}))

    # Summary
    tbl |>
        summarise(
            .by = c({{ x }}, ...),
            n = sum(!is.na({{ t }})),
            mean = mean({{ t }}, na.rm = TRUE),
            p50 = median({{ t }}, na.rm = TRUE),
            sd = sd({{ t }}, na.rm = TRUE),
            min = min({{ t }}, na.rm = TRUE),
            max = max({{ t }}, na.rm = TRUE),
        ) |>
        left_join(df_n) |>
        mutate(
            p = n / N
        ) |>
        select(..., {{ x }}, n, p, mean, p50, sd, min, max)
}
```


Unless otherwise stated, the starting sample for these analyses is all Open Science Registrations (OSR).  As of `r MOST_RECENT`, there are `r format(n_distinct(reg_events$node_id), big.mark = ",")` Open Science Registrations (OSR) in the OSF.

```{r}
# Long form (among earliest connected resources of each type)
df_long <- reg_events |>
    select(node_id, registered_date, date_lifecycle, starts_with("date1_")) |>
    rename(date1_lifecycle = date_lifecycle) |>
    pivot_longer(
        cols = dplyr::matches("date1_"),
        names_to = "event",
        names_prefix = "date1_",
        values_to = "date"
    ) |>
    arrange(node_id, date)

#  Add sequencing
df_sequence <- df_long |>
    filter(event %in% c(tolower(OUTCOMES), tolower(OUTPUTS)) & !is.na(date)) |>
    group_by(node_id) |>
    arrange(date) |>
    mutate(
        sequence = row_number()
    ) |>
    ungroup() |>
    select(node_id, event, sequence)

# Time-to-Event
df_tte <- df_long |>
    left_join(df_sequence) |>
    mutate(time_to_event = as.numeric(date - registered_date, units = "days")) 
```

The following table summarizes how long it takes for an OSR to become fully lifecycle open.  Each row corresponds to three different milestones in the research project lifecycle:

1. The first linked output resource
2. The first linked outcome resource
3. The achievement of lifecycle open status

The "Prevalance" columns report the number and percentage of OSRs that have reached each milestone, while the "Distribution" columns provide summary statistics characterizing the center, spread, and range of time to each milestone (in days).

```{r}
df_summary <- tte_summarizer(df_tte, t = time_to_event, x = event)
tte_table(df_summary)
```

The following interactive graphic provides the same information via a boxplot.

```{r}
p <- df_tte |>
    filter(event %in% c("output", "outcome", "lifecycle")) |>
    mutate(
        event = stringr::str_to_title(event),
        event = factor(event, levels = c("Output", "Outcome", "Lifecycle"))
    ) |>
    ggplot() +
    geom_boxplot_interactive(
        aes(
            x = event,
            y = time_to_event,
            fill = event,
            data_id = event,
            group = event,
            tooltip = after_stat({
                paste0(
                    "Event: ", stringr::str_to_title(.data$fill),
                    "\n",
                    "\nMax: ", comma(.data$max),
                    "\nQ3: ", comma(.data$upper),
                    "\nMedian: ", comma(round(.data$middle)),
                    "\nQ1: ", comma(.data$lower),
                    "\nMin: ", comma(round(.data$min))
                )
            }),
            outlier.tooltip = paste(
                "Days: ", comma(round(time_to_event)))
            )
        ) +
        guides(fill = "none") +
        scale_y_continuous(labels = label_comma()) +
        labs(
            y = "Days",
            x = "Event",
            title = "Time to Lifecycle Open Status (in days)",
        ) +
        theme_minimal()
g <- girafe(ggobj = p)
g
```

We can disaggreate our findings further by looking at the prevalance and distribution of time for individual resources (code, data, materials, supplements, and papers).  As before, we present results via a table and an interactive boxplot.

```{r}
df_summary |>
    mutate(
        event = stringr::str_to_title(event)
    ) |>
    filter(event %in% c("Code", "Data", "Materials", "Supplements", "Papers")) |>
    gt() |>
    # Title
    tab_header(
        title = "Time to First Linked Resource (in days)",
        subtitle = paste0("Among all Open Science Registrations (OSR) with 1+ linked resource")
    ) |>
    # Column labels
    cols_label(
        event = "Event",
        n = "Count",
        p = "Percent",
        mean = "Mean",
        p50 = "Median",
        sd = "Std. Dev.",
        min = "Min",
        max = "Max"
    ) |>
    # Spanners
    tab_spanner(columns = c(n, p), label = "Prevalance") |>
    tab_spanner(columns = c(mean, p50, sd, min, max), label = "Distribution") |>
    # Value formatting
    fmt_number(columns = c(n, mean, p50, sd, min, max), decimals = 0) |>
    fmt_percent(columns = p, decimals = 1) |>
    opt_interactive(use_search = FALSE, use_pagination = FALSE) |>
    opt_horizontal_padding(0)
```

```{r}
p <- df_tte |>
    filter(event %in% c("code", "data", "materials", "supplements", "papers")) |>
    mutate(
        event = stringr::str_to_title(event)
    ) |>
    ggplot() +
    geom_boxplot_interactive(
        aes(
            x = event,
            y = time_to_event,
            fill = event,
            data_id = event,
            group = event,
            tooltip = after_stat({
                paste0(
                    "Event: ", stringr::str_to_title(.data$fill),
                    "\n",
                    "\nMax: ", comma(.data$max),
                    "\nQ3: ", comma(.data$upper),
                    "\nMedian: ", comma(round(.data$middle)),
                    "\nQ1: ", comma(.data$lower),
                    "\nMin: ", comma(round(.data$min))
                )
            }),
            outlier.tooltip = paste(
                "Days: ", comma(round(time_to_event)))
            )
        ) +
        guides(fill = "none") +
        scale_y_continuous(labels = label_comma()) +
        labs(
            y = "Days",
            x = "Event",
            title = "Time to First Linked Resource (in days)",
        ) +
        theme_minimal()
g <- girafe(ggobj = p)
g
```

The following tables looks at differences in time to lifecycle open science moments (first output, first outcome, and lifeycle open) by registry.  To ease interpretion, rows with zero counts are omitted.  Results can be sorted along any column and the search box can be used to filter results.

```{r}
df_summary_registry <- df_tte |>
    left_join(select(reg_tbl, node_id, registry), by = "node_id") |>
    tte_summarizer(t = time_to_event, x = event, registry) |>
    mutate(registry = tidy_registry_names(registry)) |>
    filter(n > 0) |>
    rename(Registry = registry) 

tte_table(tbl = df_summary_registry, title = "Time to Lifecycle Open Status by Registry (in days)", group_label = "Registry", Registry) |>
    opt_interactive(use_search = TRUE, use_pagination = FALSE) |>
    opt_horizontal_padding(0)
```


### Sequencing

There are several potential insights related to the *sequencing* of resource connections.  The following table summarizes sequencing patterns for OSRs with at least two linked resources.  The rows correspond to resource types (code, data, materials, supplements, and papers), while the columns sequencing order.

For instance, when looking within the "First" column, we see that Data is most frequently linked first (41%), followed by Papers (31%).  


```{r}
# Data
df_summary <- df_tte |>
    filter(event %in% c("code", "data", "materials", "supplements", "papers")) |> 
    filter(!is.na(sequence)) |>
    tte_summarizer(t = sequence, x = event, sequence) |>
    mutate(
        event = stringr::str_to_title(event)
    ) |>
    arrange(sequence, event) |>
    select(event, sequence, n, p) |>
    pivot_wider(
        id_cols = event,
        names_from = sequence,
        values_from = c(n, p),
        names_glue = "{.value}_{sequence}",
        values_fill = 0
    ) |>
    select(event, n_1, p_1, n_2, p_2, n_3, p_3, n_4, p_4, n_5, p_5) |>
    mutate(
        event = stringr::str_to_title(event)
    )

# Table
df_summary |>
    gt(rowname_col = "event") |>
    tab_header(
        title = "Sequence of Connected Resources",
        subtitle = paste0("Among all Open Science Registrations (OSR) [n = ", format(n_distinct(df_sequence$node_id), big.mark = ","), "]")) |>
    cols_label(
        starts_with("n_") ~ "Count",
        starts_with("p_") ~ "Percent"
    ) |>
    # Spanners
    tab_spanner(
        columns = ends_with("1"),
        label = md(glue("**First**<br>(n={comma(sum(df_summary$n_1))})"))) |>
    tab_spanner(
        columns = ends_with("2"),
        label = md(glue("**Second**<br>(n={comma(sum(df_summary$n_2))})"))) |>
    tab_spanner(
        columns = ends_with("3"),
        label = md(glue("**Third**<br>(n={comma(sum(df_summary$n_3))})"))) |>
    tab_spanner(
        columns = ends_with("4"),
        label = md(glue("**Fourth**<br>(n={comma(sum(df_summary$n_4))})"))) |>
    tab_spanner(
        columns = ends_with("5"),
        label = md(glue("**Fifth**<br>(n={comma(sum(df_summary$n_5))})"))) |>
    # Row groups
    tab_row_group(
        label = "Outputs",
        rows = OUTPUTS) |>
    tab_row_group(
        label = "Outcomes",
        rows = OUTCOMES
    ) |>
    tab_stub_indent(rows = c(OUTPUTS, OUTCOMES), indent = 3) |>
    tab_options(
        row_group.background.color = "gray95"
    ) |>
    row_group_order(
        groups = c("Outputs", "Outcomes")
    ) |>
    # Value formatting
    fmt_number(columns = starts_with("n_"), decimals = 0) |>
    fmt_percent(columns = starts_with("p_"), decimals = 1) |>
    opt_interactive()
```


### Resource Sequencing and Latency

A third potential line of inquiry explores how/whether sequence order relates to overall latency times for resource connections of different types. Due to the limited number of OSRs with all five or at least four linked resources of *any* type, the following table summarizes latency times by resource type and sequence order.

*IN PROGRESS*

```{r}
# Recompute time to event based on distance to last event
# df_summary <- df_tte |>
#     filter(event %in% c("code", "data", "materials", "supplements", "papers")) |> 
#     filter(!is.na(sequence) & sequence < 4) |>
#     group_by(node_id, event) |>
#     arrange(sequence) |>
#     mutate(
#         benchmark_date = ifelse(sequence == 1, registered_date, date),
#         time_to_event = as.numeric(date - benchmark_date, units = "days")
#     ) |>
#     ungroup()
#     tte_summarizer(x = event, t = time_to_event, event, sequence) |>
#     distinct(event, sequence, mean, p50, sd, min, max, .keep_all = TRUE) |>
#     select(-p) |>
#     arrange(event, sequence) |>
#     group_by(event) |>
#     mutate(
#         median_diff = if_else(
#             sequence == 1, p50,
#             p50 - lag(p50)),
#         mean_diff = mean - lag(mean)
#     )
# df_summary
```



<!-- 
These sorts of questions are obviously limited to OSRs with at least two connected resources, which we could subdivide further into two different sets of analyses:

- *Inter*-resource latency - Questions of interest rooted in the amount of time between connected resources of *different types* (e.g., Linking a dataset and the code that produced it)
- *Intra*-resource latency - Questions of interest rooted in the amount of time between connected resources of the *same type* (e.g., Linking multiple datasets)

#### Inter-resource latency

IN PROGRESS...

-->

## Time Series

We can also examine the efficiency of Lifecycle Open Science Registrations over time.  By efficiency, we mean the ratio of Lifecycle Open Science Registrations to Open Science Registrations.  In other words, the percentage of Open Science Registrations that meet criteria for Lifecycle Open Science.

```{r}
overall_tbl |>
    select(Date, `LOS-Reg / OSR`) |>
    pivot_longer(
        cols = c(`LOS-Reg / OSR`),
        names_to = "Metric", values_to = "Percentage") |>
    plot_time_series(Date, Percentage, .smooth = FALSE, .title = "Efficiency of Lifecycle Open Science Registrations")

```

We can also plot these percentages over time for each registry.  Because of the disparity in the number of registrations between registries, we calculate the percentage of registrations that meeting Open Science Registration criteria.  This is the `LOS-Reg / OSR` netric from the previous table.


```{r}
registry_ptbl <- registry_tbl |>
    select(Date, Registry, `LOS-Reg / OSR`) |>
    pivot_longer(
        cols = c(`LOS-Reg / OSR`),
        names_to = "Metric", values_to = "Percentage") |>
    ungroup()

registry_ptbl |>
    filter(Metric == "LOS-Reg / OSR") |>
    plot_time_series(Date, Percentage, .color_var = Registry,
    .smooth = FALSE, .title = "Efficiency of Lifecycle Open Science Registrations by Registry")
```