---
title: "OSF Registration Badges"
date: "2025-09-15"
date-modified: last-modified
---

# Overview

This vignette measures lifecycle open science on OSF by looking at open science practices linked to open science registrations.

## Definitions

> **Open Science Registration (OSR)**: An OSF Registration that is jointly *open*, *non-deprecated* and *authentic*

- Openness Criteria:
    1. Public (open-1)
    2. ~~Not Embargoed (open-2)~~

- Non-Deprecation Criteria:
    1. Registered (nondeprecated-1)
    2. Not Deleted (nondeprecated-2)
    3. Not Retracted (nondeprecated-3)

- Authenticity Criteria:
    1. Not Spam (authentic-1)


> **Lifecycle Open Science Registration (LOS-Reg)**: An OSR that represents a lifecycle open science research project.

- Lifecycle Opennness Criteria:

    1. **Outcome** - The OSR has at least 1 linked [Open Practice Badge](https://help.osf.io/article/452-open-practice-badges) from among: "Data", "Analytic Code", "Materials" or "Supplements".  
    2. **Output** - The OSR has at least 1 linked "Papers" Open Practice Badge.


# Results
```{r}
# Packages
library(arrow)
library(gt)
library(dplyr)
library(lubridate)
library(tidyr)
library(timetk)


# Modules
box::use(
  R / helpers[tidy_registry_names, tidy_template_names],
  R / plot[pivoter, factorizer, ts_prep]
)

# Data sources
all_ts <- read_parquet(here::here("data/registration_tsmonthly.parquet")) |>
    filter(date >= "2022-08-01")
registry_ts <- read_parquet(here::here("data/registration_registries_tsmonthly.parquet")) |>
    filter(date >= "2022-08-01") |>
    mutate(registry = tidy_registry_names(registry))
template_ts <- read_parquet(here::here("data/registration_templates_tsmonthly.parquet")) |>
    filter(date >= "2022-08-01") |>
    mutate(template = tidy_template_names(template)) |>
    group_by(date, template) |>
    summarise_all(sum) 

# Pivot for plots and assign labels
all_summary <- pivoter(all_ts) |>
    ts_prep()
registry_summary <- pivoter(registry_ts, registry) |>
    ts_prep()
template_summary <- pivoter(template_ts, template) |>
    ts_prep()

# Constants
MOST_RECENT_CHR <- max(all_ts$date)
MOST_RECENT <- ymd(MOST_RECENT_CHR)
TABLE_CRITERIA <- c(
    "total", "los_plan", "los_outcomes", "los_outputs", "los_complete")
TABLE_NAMES <- c(
    "Total", "Open Science Registration (OSR)", "OSR + Outcome(s)", "OSR + Output(s)",
    "Lifecycle Open Science Registration (LOS-Reg)"
)
```

## Today

Here is the current state of LOS research projects on the OSF as of `r max(all_ts$date)`.  For all of the summary tables below, the following fields are included:

- `<GROUP_NAME>`: An optional grouping variable for seeing disaggregated results (e.g., by registry, registration template, etc.)
- `Total`: Total number of OSF Registrations (no filtering at all)
- `Open Science Registration (OSR)`: Number of Open Science Registrations (i.e., Open + Non-deprecated + Authentic)
- `OSR + Outcome(s)`: Number of Open Science Registrations with at least one linked outcome badge
- `OSR + Output(s)`: Number of Open Science Registrations with at least one linked output badge
- `Lifecycle Open Science Registration (LOS-Reg)`: Number of Open Science Registrations with at least one linked outcome and at least one linked output badge
- `LOS-Reg / OSR`: Percentage of Open Science OSF Registrations (OSR) that are Lifecycle Open Science Registrations (LOS-Reg)


### Aggregate

```{r}
overall_tbl <- all_summary |>
    filter(criteria %in% TABLE_CRITERIA) |>
    pivot_wider(names_from = criteria, values_from = n) 
names(overall_tbl) <-c("Date", TABLE_NAMES)

overall_tbl <- overall_tbl |>
    mutate(
        `LOS-Reg / OSR` = `Lifecycle Open Science Registration (LOS-Reg)` / `Open Science Registration (OSR)`,
        `LOS-Reg / Total` = `Lifecycle Open Science Registration (LOS-Reg)` / Total
    )

today_gtbl <- overall_tbl |>
    filter(Date == MOST_RECENT) |>
    select(-Date, -`LOS-Reg / Total`) |>
    gt() |>
    tab_header(
        title = "Lifecycle Open Science Registrations",
        subtitle = paste0("as of ", MOST_RECENT_CHR)
    ) |>
    fmt_number(columns = c(Total:`Lifecycle Open Science Registration (LOS-Reg)`), decimals = 0) |>
    fmt_percent(columns = `LOS-Reg / OSR`, decimals = 2)

today_gtbl
```

### By Registry

```{r}
registry_tbl <- registry_summary |>
    filter(criteria %in% TABLE_CRITERIA) |>
    pivot_wider(id_cols = c(date, registry), names_from = criteria, values_from = n) 
names(registry_tbl) <-c("Date", "Registry", TABLE_NAMES)

registry_tbl <- registry_tbl |>
    mutate(
        `LOS-Reg / OSR` = `Lifecycle Open Science Registration (LOS-Reg)` / `Open Science Registration (OSR)`,
        `LOS-Reg / Total` = `Lifecycle Open Science Registration (LOS-Reg)` / Total
    )

today_registry_gtbl <- registry_tbl |>
    ungroup() |>
    filter(Date == MOST_RECENT) |>
    arrange(desc(`Lifecycle Open Science Registration (LOS-Reg)`)) |>
    select(-Date, -`LOS-Reg / Total`) |>
    gt() |>
    tab_header(
        title = "Lifecycle Open Science Registrations by Registry",
        subtitle = paste0("as of ", MOST_RECENT_CHR)
    ) |>
        fmt_number(columns = c(Total:`Lifecycle Open Science Registration (LOS-Reg)`), decimals = 0) |>
    fmt_percent(columns = `LOS-Reg / OSR`, decimals = 2)

today_registry_gtbl
```

### By Template

```{r}
template_tbl <- template_summary |>
    filter(criteria %in% TABLE_CRITERIA) |>
    pivot_wider(id_cols = c(date, template), names_from = criteria, values_from = n) 
names(template_tbl) <-c("Date", "Template", TABLE_NAMES)

template_tbl <- template_tbl |>
    mutate(
        `LOS-Reg / OSR` = `Lifecycle Open Science Registration (LOS-Reg)` / `Open Science Registration (OSR)`,
        `LOS-Reg / Total` = `Lifecycle Open Science Registration (LOS-Reg)` / Total
    )

today_template_gtbl <- template_tbl |>
    ungroup() |>
    filter(Date == MOST_RECENT) |>
    arrange(desc(`Lifecycle Open Science Registration (LOS-Reg)`)) |>
    select(-Date, -`LOS-Reg / Total`) |>
    gt() |>
    tab_header(
        title = "Lifecycle Open Science Registrations by Template",
        subtitle = paste0("as of ", MOST_RECENT_CHR)
    ) |>
        fmt_number(columns = c(Total:`Lifecycle Open Science Registration (LOS-Reg)`), decimals = 0) |>
    fmt_percent(columns = `LOS-Reg / OSR`, decimals = 2)

today_template_gtbl
```

## Time Series

We can also examine the efficiency of Lifecycle Open Science Registrations over time.  By efficiency, we mean the ratio of Lifecycle Open Science Registrations to Open Science Registrations.  In other words, the percentage of Open Science Registrations that meet criteria for Lifecycle Open Science.

```{r}
overall_tbl |>
    select(Date, `LOS-Reg / OSR`) |>
    pivot_longer(
        cols = c(`LOS-Reg / OSR`),
        names_to = "Metric", values_to = "Percentage") |>
    plot_time_series(Date, Percentage, .smooth = FALSE, .title = "Efficiency of Lifecycle Open Science Registrations")

```

We can also plot these percentages over time for each registry.  Because of the disparity in the number of registrations between registries, we calculate the percentage of registrations that meeting Open Science Registration criteria.  This is the `LOS-Reg / OSR` netric from the previous table.


```{r}
registry_ptbl <- registry_tbl |>
    select(Date, Registry, `LOS-Reg / OSR`, `LOS-Reg / Total`) |>
    pivot_longer(
        cols = c(`LOS-Reg / OSR`, `LOS-Reg / Total`),
        names_to = "Metric", values_to = "Percentage") |>
    ungroup()

registry_ptbl |>
    filter(Metric == "LOS-Reg / OSR") |>
    plot_time_series(Date, Percentage, .color_var = Registry,
    .smooth = FALSE, .title = "Efficiency of Lifecycle Open Science Registrations by Registry")
```

# CHANGELOG

- 2025-10-03
    - Disaggreagate by OSF Registration template
    - UI updates
    - Consolidated repository struture (data processing + presentation layers)

- 2025-10-01
    - Align operationalization of "outputs" and "outcomes" with organizational definitions
    - Drop counts and computations involving "Total" (i.e.,unfiltered) registrations
    - Drop non-embargoed requirement from the "Openness" criteria for Open Science Registration (OSR) status
    
- 2023-09-15: Initial version